Sara Benist MADA Project

### 2023-04-28 products/manuscript/Manuscript.qmd
Project Review-Jacob Matta

```{r}
#| label: tbl-incfithb
#| fig-cap: "Summary table for fitted linear model predicting incidence for high burden countries"
readRDS(file = here("results", "model fit tables", "incfittable.rds")) 
```
```{r}
#| label: tbl-incfit
#| fig-cap: "Summary table for fitted linear model predicting incidence"
readRDS(file = here("results", "model fit tables", "incfittableFD.rds")) 
```

@@

```{r}
#| label: tbl-mortfithb
#| fig-cap: "Summary table for fitted linear model predicting mortality for high burden countries"
readRDS(file = here("results", "model fit tables", "mortfittable.rds"))
```
```{r}
#| label: tbl-mortfit
#| fig-cap: "Summary table for fitted linear model predicting mortality"
readRDS(file = here("results", "model fit tables", "mortfittableFD.rds"))
```

@@

```{r}
#| label: tbl-prevfithb
#| fig-cap: "Summary table for fitted linear model predicting prevalence for high burden countries"
readRDS(file = here("results", "model fit tables", "prevfittable.rds"))
```
```{r}
#| label: tbl-prevfit
#| fig-cap: "Summary table for fitted linear model predicting prevalence"
readRDS(file = here("results", "model fit tables", "prevfittableFD.rds")) 
```

@@

```{r}
#| label: fig-prediction
#| fig-cap: "Prediction plot estimating TB incidence for females and males in Central African Republic"
readRDS(file = here("results", "model fit tables", "prediction1.rds")) 
```

@@

The @tbl-treeinc displays an example of the model tuning for decision tree model predicting incidence, and @tbl-treeinchb shows the same method for high burden countries. Please refer to the `statistical_analysis.qmd` for the full code and results on modelling.
```{r}
#| label: tbl-treeinc
#| fig-cap: "Summary table for fitted tree model predicting incidence"
readRDS(file = here("results", "tune plots", "wdinctreeplot.rds")) 
```

```{r}
#| label: tbl-treeinchb
#| fig-cap: "Summary table for fitted linear model predicting incidence for high burden countries"
readRDS(file = here("results", "tune plots", "hbinctreeplot.rds"))
```

>>>>

```{r}
#| label: tbl-incfithb
#| fig-cap: "Summary table for fitted linear model predicting incidence for high burden countries"
readRDS(file = here("results", "statistical_analysis", "model fit tables", "incfittable.rds")) 
```

```{r}
#| label: tbl-incfit
#| fig-cap: "Summary table for fitted linear model predicting incidence"
readRDS(file = here("results", "statistical_analysis","model fit tables", "incfittableFD.rds")) 
```

@@

```{r}
#| label: tbl-mortfithb
#| fig-cap: "Summary table for fitted linear model predicting mortality for high burden countries"
readRDS(file = here("results", "statistical_analysis", "model fit tables", "mortfittable.rds"))
```
```{r}
#| label: tbl-mortfit
#| fig-cap: "Summary table for fitted linear model predicting mortality"
readRDS(file = here("results","statistical_analysis", "model fit tables", "mortfittableFD.rds"))
```

@@

```{r}
#| label: tbl-prevfithb
#| fig-cap: "Summary table for fitted linear model predicting prevalence for high burden countries"
readRDS(file = here("results","statistical_analysis", "model fit tables", "prevfittable.rds"))
```
```{r}
#| label: tbl-prevfit
#| fig-cap: "Summary table for fitted linear model predicting prevalence"
readRDS(file = here("results", "statistical_analysis", "model fit tables", "prevfittableFD.rds")) 
```

@@

```{r}
#| label: fig-prediction
#| fig-cap: "Prediction plot estimating TB incidence for females and males in Central African Republic"
readRDS(file = here("results", "statistical_analysis", "model fit tables", "prediction1.rds")) 
```

@@

The @tbl-treeinc displays an example of the model tuning for decision tree model predicting incidence, and @tbl-treeinchb shows the same method for high burden countries. Please refer to the `statistical_analysis.qmd` for the full code and results on modelling.
```{r}
#| label: tbl-treeinc
#| fig-cap: "Summary table for fitted tree model predicting incidence"
readRDS(file = here("results", "statistical_analysis","tune plots", "wdinctreeplot.rds")) 
```

```{r}
#| label: tbl-treeinchb
#| fig-cap: "Summary table for fitted linear model predicting incidence for high burden countries"
readRDS(file = here("results", "statistical_analysis","tune plots", "hbinctreeplot.rds"))
```
